Leveraging the VTA-TVM Hardware-Software Stack \\for FPGA Acceleration of 8-bit ResNet-18 Inference

### 2018-06-13 dissemination.publication/9375838469ad4029/paper.tex
pass on ck flow

Our artifact is fully contained under: \url{https://github.com/uwsaml/vta}.
Our repository contains README.md instructions on how to deploy, and reproduce the software and hardware artifacts on the Pynq FPGA development platform.

@@

Reproducing the examples requires Python, Numpy, MxNet, NNVM (\url{nnvm.tvmlang.org}) and TVM installed. We describe the installation process in the VTA Github repo README files.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evaluation and expected result}
We describe the experimental metrics of our artifact below:
\begin{itemize}
\item Single batch inference time: 0.42s
\item Top-1 accuracy: 37\%
\item Top-5 accuracy: 63\%
\item Power consumption: peak 2W for SoC
\item Device cost: \$65 for academics (at the time of the paper submission), \$200 otherwise
\end{itemize}

@@

\begin{verbatim}
$ ck pull repo:ck-request-asplos18-mobilenets-tvm-arm
\end{verbatim}

@@

Please follow this [getting started guide]() to set up your Pynq board.

>>>>

Our artifact is fully contained under: \url{https://github.com/uwsaml/vta}.
Our repository contains instructions on how to deploy, and reproduce the software and hardware artifacts on the Pynq FPGA development platform.

@@

Reproducing the examples requires Python, Numpy, MxNet, NNVM (\url{nnvm.tvmlang.org}) and TVM  (\url{tvm.ai}) installed. We describe the installation process in the VTA Github repo README files.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evaluation and expected result}
We describe the experimental metrics of our artifact below:
\begin{itemize}
\item Single batch inference time: 0.42s.
\item Top-1 accuracy: 37\%.
\item Top-5 accuracy: 63\%.
\item Power consumption: peak 2W for SoC.
\item Device cost: \$65 for academics (at the time of the paper submission), \$200 otherwise.
\end{itemize}

@@

\begin{verbatim}
$ ck pull repo:ck-request-asplos18-resnet-tvm-fpga
\end{verbatim}

@@

Please follow this getting-started guide (\url{https://github.com/uwsaml/vta/tree/master/apps/pynq_rpc}) to set up your Pynq board.
